R, Python, and Ruby clients for GBIF species occurrence data

### 2017-10-04 manuscript.Rmd
comma between R and Python in title needed

---
layout: review, 11pt
linenumbers: true
title: "R Python, and Ruby clients for GBIF species occurrence data"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: scott(at)ropensci.org
    footnote: Corresponding author
  - name: Carl Boettiger
    affiliation: boettig
    email: carl(at)ropensci.org
address:
  - code: cstar
    address: |
      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA
  - code: boettig
    address: |
      rOpenSci, Department of Enivornmental Science, Policy and Management, University of California, Berkeley, CA, USA
abstract: |
      Corresponding Author:

>>>>

---
layout: review, 11pt
linenumbers: true
title: "R, Python, and Ruby clients for GBIF species occurrence data"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: scott(at)ropensci.org
    footnote: Corresponding author
  - name: Carl Boettiger
    affiliation: boettig
    email: carl(at)ropensci.org
address:
  - code: cstar
    address: |
      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA
  - code: boettig
    address: |
      rOpenSci, Department of Enivornmental Science, Policy and Management, University of California, Berkeley, CA, USA
abstract: |
      Corresponding Author:
